----
README for the publication: The Impact of Declining HIV Testing in Africa on Time to HIV Diagnosis and Awareness of HIV Status: A Modeling Study of Population-Based Surveys and HIV Testing Program Data (2015–2023)

The goal of Shiny90 is to provide annual estimates of the proportion of people living with HIV (PLHIV) who are aware of their status by combining estimates of PLHIV from EPP/Spectrum, annual programmatic data on the number of HIV tests performed (and test yield), and nationally representative surveys of HIV testing behaviors.

This is an update to Shiny90 that includes ANC estimates for the publication, as well as a counterfactual analysis to estimate the impact of reductions in testing.
----
This script was tested and is intended to work only on Windows. The package used to perform parallel computations is not functional on macOS.
----
This script was tested on two computers:

specs PC1:
OS: Windows 11
CPU: i9-13900H, 2600 Mhz, 14 Core(s), 20 Logical Processor(s)
Ram: 16 GB 4800 mhz
Drive: 1tb SSD
Graphics: Intel Iris(R) Xe Graphic 8 GB

spec PC2:
OS: Windows 10
CPU: i7-8700, 3200 Mhz, 6 Core(s), 12 Logical Processor(s)
Ram: 16 GB 2666 mhz
Drive: 1tb SSD
Graphics: NVIDIA GeForce GTX 1050 12GB

Both were tested on:
R version 4.5.2
RStudio-2026.01.1-403
rtools 4.5
----
goal: download and install required packages, load source files
runtime: ~187 seconds (with no packages installed)
----
```{r setup, include = FALSE}

packages <- c(
  "scales", "tidyverse", "rnaturalearth", "rnaturalearthdata",
  "sf", "ggnewscale", "devtools", "data.table", "Matrix", "Rcpp",
  "stringi", "ggh4x", "forcats", "ggtext", "terra", "gridExtra"
)
to_install <- packages[!packages %in% installed.packages()[, "Package"]]

if (length(to_install) > 0) {
  install.packages(to_install)
}
# load all packages
invisible(lapply(packages, library, character.only = TRUE))

# download and set up first 90 package
# first90
if(!"first90" %in% installed.packages()[, "Package"]){
 devtools::install_github("mrc-ide/first90release")
}
library(first90)

# source functions
source(here::here("0.1 extracting pjnz functions.R"))
source(here::here("0.4 functions.R"))
source(here::here("0.5 simul-aware-functions.R"))
source(here::here("0.6 time dx functions.R"))

source(here::here("1.0 simmod.R"))
source(here::here("1.1 tot test out.R"))

# create data directory:
if (!dir.exists("data")) {
  dir.create("data", recursive = TRUE)
}

```

----
goal: load example synthetic file (based off Malawi)
runtime : 5 seconds
comment: for analysis of full PJNZ files use "ReadMe - real PJNZ"
----
```{r inital loading, fig.height = 8, fig.width = 8, warning = FALSE}

# load pre cleaned synthethic file
Synthetic <- readRDS(here::here("example files.rds"))

# align naming scheme with files
make_country <- list()
make_country$Synthetic <- Synthetic$make_country

pmtct_list <- list()
pmtct_list$Synthetic <- Synthetic$pmtct

hivdemo_proj_list <- list()
hivdemo_proj_list$Synthetic <- Synthetic$demo_proj 

# extract fp 
fp <- make_country$Synthetic$fp

# We visualize the PJNZ data
first90::plot_pjnz(fp)

#define input data
age_group <- c('15-24','25-34','35-49')
cnt = make_country$Synthetic$cnt

# define clean suvery and program Synthetic
dat <- first90::select_hts(make_country$Malawi$survey_hts, cnt, age_group)

prg_dat <- first90::select_prgmdata(make_country$Synthetic$prgm_dat, cnt, age_group)

# We visualize the program data
first90::plot_inputdata(prg_dat, fp)

```


----
goal: Perform optimization of example data set
estimate: 797-1498 seconds
comments: Nedler-Mead is used as a stochastic searching tool, some estimates may vary
outputs: optimized "make_country" file with a hessian
----
```{r simulation}


# fit the example model to example data (see 2.0 simulating Shiny90.R)

# define path
path_anc <- here::here("anc testing")

# select which country you want to run - in this case Synthetic
country = make_country$Synthetic

# confirm
cnt = country$cnt
print(cnt)
age_group <- c('15-24','25-34','35-49')

# extract fp and data
fp <- make_country[[cnt]]$fp
pgrm_dat <- first90::select_prgmdata(make_country[[cnt]]$prgm_dat, cnt = cnt)
survey_hts <- first90::select_hts(make_country[[cnt]]$survey_hts,
                                  cnt = cnt,
                                  age_group = age_group)


# select country specific pmtct
pmtct <- pmtct_list[[cnt]]


# select country specific demo proj
hivdemo_proj <- hivdemo_proj_list[[cnt]]


# the shiny90-ANC used 3 more parameters than Shiny90 add them manually
# Extract theta0 from first90 but add 2 more parameters
data("theta0", package = "first90")
theta1 = theta0
theta1[1:52] = c(theta0, theta0[1:3])

# create an initial projection
fp <- create_anc_param(
  theta = theta1,
  fp = fp,
  pmtct = pmtct,
  hivdemo_proj = hivdemo_proj,
  verbose = T
)

# curate data for likelihood from the inital projection, Avoids double counting
likdat <- prepare_anc_likdat(dat_evertest = survey_hts,
                             dat_prg = pgrm_dat,
                             fp = fp)

# estimate initial liklihood 
ll_hts_anc(
  theta = theta1,
  fp = fp,
  likdat = likdat,
  pmtct = pmtct,
  hivdemo_proj = hivdemo_proj,
  verboise = T
)

# preoptimization with Nelder-Mead to find BFGS start point (adjust based on country)
# required as BFGS can at times get lost in decision space
opt <- optim(
  theta1,
  ll_hts_anc,
  fp = fp,
  likdat = likdat,
  pmtct = pmtct,
  hivdemo_proj = hivdemo_proj,
  method = "Nelder-Mead",
  control = list(
    fnscale = -1,
    trace = 4,
    REPORT = 1,
    maxit = 1000
  )
)

# isolate optmized parameters
theta1 = opt$par

# recreate inital param from nelder-mead optimized parameters
fp <- create_anc_param(
  theta = theta1,
  fp = fp,
  pmtct = pmtct,
  hivdemo_proj = hivdemo_proj,
  verbose = T
)

# recreate likdat
likdat <- prepare_anc_likdat(dat_evertest = survey_hts,
                             dat_prg = pgrm_dat,
                             fp = fp)

# use independent opt1 vs opt again here to prevent some bugs
# BFGS much better at finalizing the optimization, it is also able to calculate the hessian( required for CrI's)
opt1 <- optim(
  theta1,
  ll_hts_anc,
  fp = fp,
  likdat = likdat,
  pmtct = pmtct,
  hivdemo_proj = hivdemo_proj,
  method = "BFGS",
  control = list(
    fnscale = -1,
    trace = 4,
    REPORT = 1,
    maxit = 550
  ),
  hessian = T
)

# reset the opt1 to opt for future steps
opt = opt1

# confirm reasonable values for opt
optimized_par_anc(opt)

# confirm liklihood matches with optim run ( an is reasonable)
ll_hts_anc(
  theta = opt$par,
  fp = fp,
  likdat = likdat,
  pmtct = pmtct,
  hivdemo_proj = hivdemo_proj,
  verboise = T
)

# fp and mod from optimized parameters
fp <- create_anc_param(
  theta = opt$par,
  fp = fp,
  pmtct = pmtct,
  hivdemo_proj = hivdemo_proj
)
mod <- simmod_anc_t(fp)

```

----
goal: calculate credible intervals from hessian
estimate: 224-360 seconds
comments: saves random sample (samp) to allow for comparison against counter factual
outputs: credible intervals for optimized model, saves file for later use
----
```{r credible intervals}

# identify credible intervals
simul <- simul.test.anc(
  opt = opt,
  fp = fp,
  likdat = likdat,
  pmtct = pmtct,
  hivdemo_proj = hivdemo_proj,
  sim = 3000
)

# save both the simul and the sample( useful for counterfactual analysis)
samp = simul$samp
simul = simul$simul

# obtaining outputs and plotting them
make_country[[cnt]]$mod <- mod
make_country[[cnt]]$fp <- fp
make_country[[cnt]]$simul <- simul
make_country[[cnt]]$out_evertest <- get_out_evertest(mod, fp)
make_country[[cnt]]$opt <- opt
make_country[[cnt]]$samp <- samp

# save the file
saveRDS(object = make_country, file = here::here('data/make_country_simul_readme.rds'))

```

----
goal: visualize model fits. Survey data ("have you ever been tested for HIV") by age and sex. Program data by anc and non-anc
estimate: ~ 10 seconds 
comments: some error may be present due to stochastic runs of nelder-mead, if too different from provided sample rerun prior 2 steps
outputs: graphs of model fit, should match graphs in data_visualizations folder
----
```{r visualization 1, fig.height = 10, fig.width = 8.5, warning = FALSE}

# total vct tests
graph_tot_tests(
  make_country[[cnt]],
  cnt = cnt,
  sex = "both",
  hivstatus = "all",
  test_type = "vcttests",
  year_start = 2000,
  year_end = 2023
)

# total VCT positives
graph_tot_tests(
  make_country[[cnt]],
  cnt = cnt,
  sex = "both",
  hivstatus = "positive",
  test_type = "vcttests",
  year_start = 2000,
  year_end = 2023
)

# total ANC
graph_tot_tests(
  make_country[[cnt]],
  cnt = cnt,
  sex = "both",
  hivstatus = "all",
  test_type = "anctests",
  year_start = 2000,
  year_end = 2023
)

# total ANC positives
graph_tot_tests(
  make_country[[cnt]],
  cnt = cnt,
  sex = "both",
  hivstatus = "positive",
  test_type = "anctests",
  year_start = 2000,
  year_end = 2023
)

# create a survey plot of all 6 age and sex groups
# this should have the full malawi simulation file from the prior steps
survey_fit_all(make_country, cnt = "Synthetic")

survey_fit_postive(make_country, cnt = "Synthetic")

```

----
goal: create the counterfactual with credible intervals
estimate: ~ 236-337 seconds seconds
comments: this calls the script "2.1 counterfactual creation" rather than rewrite the code
outputs: counterfactual files, both identifies when declines occur and simulates counterfactual CrI's
----
```{r, fig.height = 5, fig.width = 5, warning = FALSE}

# create a counterfactual
source("2.1 counterfactual creation.R")
# this fucntion resets cnt need to readd malawi
cnt = "Synthetic"

#load the files
counter_years <- readRDS("data/counter_years.rds")
counter_anc_years <- readRDS("data/counter_years.rds")


# repeat many of the inital steps, which are now saved in make country
fp <- make_country[[cnt]]$fp
pgrm_dat <- first90::select_prgmdata(make_country[[cnt]]$prgm_dat, cnt = cnt)
survey_hts <- first90::select_hts(make_country[[cnt]]$survey_hts,
                                  cnt = cnt,
                                  age_group <- c('15-24', '25-34', '35-49'))
mod = make_country[[cnt]]$mod
opt = make_country[[cnt]]$opt

# select country specific pmtct
pmtct <- pmtct_list[[cnt]]

# select country specific demo proj
hivdemo_proj <- hivdemo_proj_list[[cnt]]


# we saved the sample in the full run now we use it again( for creation of a counterfactual simulation)
samp = make_country[[cnt]]$samp

# specifies that we only care about Malawi
counter_years_loop = counter_years[counter_years$country == cnt, ]
counter_years_loop <- counter_years_loop[!is.na(counter_years_loop$country),]

#clear all counter factual sample and pmtct
samp_1 = NULL
pmtct_1 = NULL

if (!is.na(counter_years_loop$start)) {
  
  # Apply counterfactual opperation to every row of samp
  samp_new <- function(samp, counter_years_loop) {
    stopifnot(is.matrix(samp) || is.data.frame(samp))
    
    samp <- as.matrix(samp)
    
    convert <- (ncol(samp) - 4) / 2
    
    start <- as.numeric(counter_years_loop[2])
    
    # if NA, end becomes 30(ie no recovery)
    end <- as.numeric(ifelse(!is.na(counter_years_loop[3]), (
      as.numeric(counter_years_loop[3]) - 30 - 1
    ), 30))
    
    start_female <- start - 30
    start_dx     <- convert + (start - 40)
    end_dx       <- start_dx + (end - start_female)
    
    clamp <-
      function(i)
        max(1, min(ncol(samp), as.integer(i)))
    
    sf <- clamp(start_female)
    e1 <- clamp(min(end, convert))
    
    sd <- clamp(start_dx)
    e2 <- clamp(min(end_dx, convert + convert - 10))
    
    # apply to all rows
    if (sf <= e1)
      samp[, sf:e1] <- samp[, sf]
    if (sd <= e2)
      samp[, sd:e2] <- samp[, sd]
    
    samp
  }
  if (!is.na(counter_years_loop$start)) {
    samp_1 = samp_new(samp, counter_years_loop)
  } else{
    print("non-counter samp")
    samp_1 = samp
  }
  if (is.na(counter_years_loop$start) &
      is.na(counter_years_loop[1:3]$start)) {
    print("skipping")
    next
  }
  
  #counterfactual ANC
  
  start_anc = counter_years_loop$start
  
  names(pmtct$anc_test) = as.character(2000:2030)
  names(pmtct$needpmtct) = as.character(1970:2030)
  names(pmtct$receivepmtct) = as.character(1970:2030)
  
  pmtct_1 = pmtct
  
  # find the number of years which have data, using testing data
  anc_indx_years <-
    pmtct$anc_test[!is.na(pmtct$anc_test[2, ])]
  anc_data_years <-
    as.integer(names(pmtct$anc_test)[!(is.na(pmtct$anc_test[2, ]) |
                                         pmtct$anc_test[2, ] == 0)])
  anc_data_idx <-
    fp$ss$PROJ_YEARS - ((fp$ss$PROJ_YEARS + 1970 - 1) - anc_data_years)
  
  # Find valid columns where row 2 is not NA
  valid_cols <-
    which(!(is.na(pmtct$anc_test[2, ]) |
              pmtct$anc_test[2, ] == 0))  # Faster than repeated indexing
  
  # anc tested and tested anc pos
  anc_tested <-
    as.integer(colSums(pmtct$anc_test[c(2, 5), valid_cols], na.rm = T))
  anc_pos <- as.integer(pmtct$anc_test[3, valid_cols])
  
  # Extract birth indices
  births_idx <- colnames(pmtct$anc_test)[valid_cols]
  
  # Compute ANC coverage,  nb women tested at anc1 / births
  anc_cov <- anc_tested / pmtct$births[births_idx]
  
  # Compute ANC positive proportion
  anc_pos_prop <- anc_pos / anc_tested
  
  anc_tests_prob = as.numeric(pmtct$receivepmtct) / as.numeric(pmtct$needpmtct)
  anc_tests_prob[is.na(anc_tests_prob)] <- 0
  names(anc_tests_prob) <-
    fp$ss$proj_start:(fp$ss$proj_start + fp$ss$PROJ_YEARS - 1)
  
  #if (any(anc_tests_prob > 1)) { print("check spectrum's pmtct inputs, prob of being tested at anc >100%") }
  anc_tests_prob[anc_tests_prob > 1] <-
    0.999 # or we could put a default of 95% (to discuss)
  
  # linear interpolation to remove any missing data
  if (length(anc_cov) != 0) {
    # apply known data
    anc_tests_prob[anc_data_idx] <- anc_cov
    
    # predict using artcov method past the date (for projection)
    anc_tests_prob[max(anc_data_idx):fp$ss$PROJ_YEARS] <-
      anc_tests_prob[max(anc_data_idx):fp$ss$PROJ_YEARS]
    
    
  }
  # identify years when ANC should be applied
  Years_anc = names(which(anc_tests_prob[start_anc] > anc_tests_prob[start_anc:61]))
  year_start = names(anc_tests_prob[start_anc])
  #fixes some issues with country files
  
  
  if (length(Years_anc) > 0) {
    # adjust anctest
    pmtct_1$anc_test[, Years_anc] = pmtct$anc_test[, year_start]
    # if needed adjust recive/need pmtct, all countries should have anctest but just incase one year is missing.
    pmtct_1$receivepmtct[Years_anc] = pmtct$receivepmtct[year_start]
    pmtct_1$needpmtct[Years_anc] = pmtct$needpmtct[year_start]
  }
}

# run to create the counterfactual fp
fp = create_anc_param(opt$par, fp, pmtct, hivdemo_proj)


# identify credible intervals of counterfactual (need fp)
counter_simul <- simul.run.anc(samp_1, fp, pmtct = pmtct_1, hivdemo_proj = hivdemo_proj)

#save counterfactual
make_country[[cnt]]$counter_simul = counter_simul
make_country[[cnt]]$counter_samp = samp_1

# save again 
saveRDS(
  object = make_country,
  file = here::here('data/make_country_simu_final_readme.rds')
)

```

----
goal: simulates life tables for time to diagnoses and status awareness
estimate: 1191 (~20 minutes) - 2077 (~40 minutes) seconds 
comments: This is a long chunk of code exceeding 20 minutes of computing time on a high end laptop, may take significantly longer the fewer cores are available, your computer will not be usable during this step
######
comments2: if you have an error message about core usage, manually adjust the parallel::detectcores() line in the "0.5 simul-aware-functions.R" and "0.6 time dx functions.R"  files, leave at least 1 core free, at the moment it uses 3/4 of cores on the system
######
outputs: time to diagnoses and status awareness files
----
```{r time to diagnoses}
# reloads here incase a core count adjustment was required
source(here::here("0.5 simul-aware-functions.R"))
source(here::here("0.6 time dx functions.R"))


cnt = "Synthetic"

# this functions by creating a counterfactual sample then runnign all time to diangoses on that sample and 

#define time to diagnoses lists
tdx_agg_simul_male = list()
tdx_agg_simul_female = list()
tdx_agg_simul_both = list()

tdx_agg_simul_male_counter = list()
tdx_agg_simul_female_counter = list()
tdx_agg_simul_both_counter = list()

aware_agg_simul_male = list()
aware_agg_simul_female = list()
aware_agg_simul_both = list()

aware_agg_simul_male_counter = list()
aware_agg_simul_female_counter = list()
aware_agg_simul_both_counter = list()

# cannot run chad without changing see 2.3 time to diangoses
# ensure it is still malawi
print(cnt)

#ensure all data frames are clean
simul_b_counter = NULL
simul_b_counter = NULL
simul_b_counter = NULL

simul_f = NULL
simul_m = NULL
simul_b = NULL

simul_tdxM_counter = NULL
simul_tdxF_counter = NULL
simul_tdxB_counter = NULL

simul_tdxM = NULL
simul_tdxF = NULL
simul_tdxB = NULL


# define variable again
fp <- make_country[[cnt]]$fp

pgrm_dat <-
  first90::select_prgmdata(make_country[[cnt]]$prgm_dat, cnt = cnt)

survey_hts <-
  first90::select_hts(
    make_country[[cnt]]$survey_hts,
    cnt = cnt,
    age_group = c('15-24', '25-34', '35-49')
  )

# define parameters by country
samp = make_country[[cnt]]$samp
opt = make_country[[cnt]]$opt
mod = make_country[[cnt]]$mod

# we select pmtct data
pmtct <- pmtct_list[[cnt]]

names(pmtct$receivepmtct) = as.character(1970:2030)
names(pmtct$needpmtct) = as.character(1970:2030)

# we select HIV demo proj
hivdemo_proj <- hivdemo_proj_list[[cnt]]

# repeat again to create a new counterfatual sample
#clear all counter factual sample and pmtct
samp_1 = NULL
pmtct_1 = NULL

if (!is.na(counter_years_loop$start)) {
  
  samp_1 <- make_country[[cnt]]$counter_samp
  
  #counterfactual ANC
  start_anc = counter_years_loop$start
  
  names(pmtct$anc_test) = as.character(2000:2030)
  names(pmtct$needpmtct) = as.character(1970:2030)
  names(pmtct$receivepmtct) = as.character(1970:2030)
  
  pmtct_1 = pmtct
  
  # find the number of years which have data, using testing data
  anc_indx_years <-
    pmtct$anc_test[!is.na(pmtct$anc_test[2, ])]
  anc_data_years <-
    as.integer(names(pmtct$anc_test)[!(is.na(pmtct$anc_test[2, ]) |
                                         pmtct$anc_test[2, ] == 0)])
  anc_data_idx <-
    fp$ss$PROJ_YEARS - ((fp$ss$PROJ_YEARS + 1970 - 1) - anc_data_years)
  
  # Find valid columns where row 2 is not NA
  valid_cols <-
    which(!(is.na(pmtct$anc_test[2, ]) |
              pmtct$anc_test[2, ] == 0))  # Faster than repeated indexing
  
  # anc tested and tested anc pos
  anc_tested <-
    as.integer(colSums(pmtct$anc_test[c(2, 5), valid_cols], na.rm = T))
  anc_pos <- as.integer(pmtct$anc_test[3, valid_cols])
  
  # Extract birth indices
  births_idx <- colnames(pmtct$anc_test)[valid_cols]
  
  # Compute ANC coverage,  nb women tested at anc1 / births
  anc_cov <- anc_tested / pmtct$births[births_idx]
  
  # Compute ANC positive proportion
  anc_pos_prop <- anc_pos / anc_tested
  
  anc_tests_prob = as.numeric(pmtct$receivepmtct) / as.numeric(pmtct$needpmtct)
  anc_tests_prob[is.na(anc_tests_prob)] <- 0
  names(anc_tests_prob) <-
    fp$ss$proj_start:(fp$ss$proj_start + fp$ss$PROJ_YEARS - 1)
  
  #if (any(anc_tests_prob > 1)) { print("check spectrum's pmtct inputs, prob of being tested at anc >100%") }
  anc_tests_prob[anc_tests_prob > 1] <-
    0.999 # or we could put a default of 95% (to discuss)
  
  # linear interpolation to remove any missing data
  if (length(anc_cov) != 0) {
    # apply known data
    anc_tests_prob[anc_data_idx] <- anc_cov
    
    # predict using artcov method past the date (for projection)
    anc_tests_prob[max(anc_data_idx):fp$ss$PROJ_YEARS] <-
      anc_tests_prob[max(anc_data_idx):fp$ss$PROJ_YEARS]
    
    
  }
  # identify years when ANC should be applied
  Years_anc = names(which(anc_tests_prob[start_anc] > anc_tests_prob[start_anc:61]))
  year_start = names(anc_tests_prob[start_anc])
  #fixes some issues with country files
  
  
  if (length(Years_anc) > 0) {
    # adjust anctest
    pmtct_1$anc_test[, Years_anc] = pmtct$anc_test[, which(names(pmtct$anc_test) %in% year_start)]
    # if needed adjust recive/need pmtct, all countries should have anctest but just incase one year is missing.
    pmtct_1$receivepmtct[which(names(pmtct$anc_test) %in% Years_anc)] = pmtct$receivepmtct[which(names(pmtct$anc_test) %in% year_start)]
    pmtct_1$needpmtct[which(names(pmtct$anc_test) %in% Years_anc)] = pmtct$needpmtct[which(names(pmtct$anc_test) %in% year_start)]
  }
}


# time to diagnosis
simul_tdxF = simul_pool_time_dx_agg_prev(
  samp = samp,
  mod = make_country[[cnt]]$mod,
  fp = make_country[[cnt]]$fp,
  hivdemo_proj = hivdemo_proj_list[[cnt]],
  pmtct = pmtct_list[[cnt]],
  year = 2015:2023,
  std = F,
  age = c("15-24", "25-34", "35-49", "50-99"),
  sex = "female",
  parallel = T
)
print(1)
simul_tdxM = simul_pool_time_dx_agg_prev(
  samp = samp,
  mod = make_country[[cnt]]$mod,
  fp = make_country[[cnt]]$fp,
  hivdemo_proj = hivdemo_proj_list[[cnt]],
  pmtct = pmtct_list[[cnt]],
  year = 2015:2023,
  std = F,
  age = c("15-24", "25-34", "35-49", "50-99"),
  sex = "male",
  parallel = T
)

print(2)

simul_tdxB = simul_pool_time_dx_agg_prev(
  samp = samp,
  mod = make_country[[cnt]]$mod,
  fp = make_country[[cnt]]$fp,
  hivdemo_proj = hivdemo_proj_list[[cnt]],
  pmtct = pmtct_list[[cnt]],
  year = 2015:2023,
  std = F,
  age = c("15-24", "25-34", "35-49", "50-99"),
  sex = c("male", "female"),
  parallel = T
)
print(3)

tdx_agg_simul_male[[cnt]]$out_simul_tdx_all = simul_tdxM
tdx_agg_simul_female[[cnt]]$out_simul_tdx_all = simul_tdxF
tdx_agg_simul_both[[cnt]]$out_simul_tdx_all = simul_tdxB

make_country[[cnt]]$tdx_male$out_simul_tdx_all = simul_tdxM
make_country[[cnt]]$tdx_female$out_simul_tdx_all = simul_tdxF
make_country[[cnt]]$tdx_both$out_simul_tdx_all = simul_tdxB

gc()


# counterfactual time to diagnosis
if (!(is.null(samp_1))) {
  simul_tdxF_counter = simul_pool_time_dx_agg_prev(
    samp = samp_1,
    mod = make_country[[cnt]]$mod,
    fp = make_country[[cnt]]$fp,
    hivdemo_proj = hivdemo_proj_list[[cnt]],
    pmtct = pmtct_1,
    year = 2015:2023,
    std = F,
    age = c("15-24", "25-34", "35-49", "50-99"),
    sex = "female",
    parallel = T
  )
  
  print(4)
  
  simul_tdxM_counter = simul_pool_time_dx_agg_prev(
    samp = samp_1,
    mod = make_country[[cnt]]$mod,
    fp = make_country[[cnt]]$fp,
    hivdemo_proj = hivdemo_proj_list[[cnt]],
    pmtct = pmtct_1,
    year = 2015:2023,
    std = F,
    age = c("15-24", "25-34", "35-49", "50-99"),
    sex = "male",
    parallel = T
  )
  
  print(5)
  
  simul_tdxB_counter = simul_pool_time_dx_agg_prev(
    samp = samp_1,
    mod = make_country[[cnt]]$mod,
    fp = make_country[[cnt]]$fp,
    hivdemo_proj = hivdemo_proj_list[[cnt]],
    pmtct = pmtct_1,
    year = 2015:2023,
    std = F,
    age = c("15-24", "25-34", "35-49", "50-99"),
    sex = c("male", "female"),
    parallel = T
  )
  
  print(6)
  
  tdx_agg_simul_male_counter[[cnt]]$out_simul_tdx_all = simul_tdxM_counter
  tdx_agg_simul_female_counter[[cnt]]$out_simul_tdx_all = simul_tdxF_counter
  tdx_agg_simul_both_counter[[cnt]]$out_simul_tdx_all = simul_tdxB_counter
  
  make_country[[cnt]]$tdx_male_counter$out_simul_tdx_all = simul_tdxM_counter
  make_country[[cnt]]$tdx_female_counter$out_simul_tdx_all = simul_tdxF_counter
  make_country[[cnt]]$tdx_both_counter$out_simul_tdx_all = simul_tdxB_counter
  
  gc()
}

simul_m <-
  simul_aware_agg(
    samp = samp,
    mod = make_country[[cnt]]$mod,
    fp = make_country[[cnt]]$fp,
    hivdemo_proj = hivdemo_proj_list[[cnt]],
    pmtct = pmtct_list[[cnt]],
    year = c(2015:2023),
    age = c("15-24", "25-34", "35-49", "50-99"),
    sex = c("male")
  )
print(7)
simul_f <-
  simul_aware_agg(
    samp = samp,
    mod = make_country[[cnt]]$mod,
    fp = make_country[[cnt]]$fp,
    hivdemo_proj = hivdemo_proj_list[[cnt]],
    pmtct = pmtct_list[[cnt]],
    year = c(2015:2023),
    age = c("15-24", "25-34", "35-49", "50-99"),
    sex = c("female")
  )
print(8)
simul_b <-
  simul_aware_agg(
    samp = samp,
    mod = make_country[[cnt]]$mod,
    fp = make_country[[cnt]]$fp,
    hivdemo_proj = hivdemo_proj_list[[cnt]],
    pmtct = pmtct_list[[cnt]],
    year = c(2015:2023),
    age = c("15-24", "25-34", "35-49", "50-99"),
    sex = c("male", "female")
  )
print(9)

aware_agg_simul_male[[cnt]]$out_simul_aware_all = simul_m
aware_agg_simul_female[[cnt]]$out_simul_aware_all = simul_f
aware_agg_simul_both[[cnt]]$out_simul_aware_all = simul_b

make_country[[cnt]]$aware_male$out_simul_aware_all = simul_m
make_country[[cnt]]$aware_female$out_simul_aware_all = simul_f
make_country[[cnt]]$aware_both$out_simul_aware_all = simul_b

gc()

# counterfactual simul
if (!(is.null(samp_1))) {
  simul_m_counter <-
    simul_aware_agg(
      samp = samp_1,
      mod = make_country[[cnt]]$mod,
      fp = make_country[[cnt]]$fp,
      hivdemo_proj = hivdemo_proj_list[[cnt]],
      pmtct = pmtct_1,
      year = c(2015:2023),
      age = c("15-24", "25-34", "35-49", "50-99"),
      sex = c("male")
    )
  
  print(10)
  
  simul_f_counter <-
    simul_aware_agg(
      samp = samp_1,
      mod = make_country[[cnt]]$mod,
      fp = make_country[[cnt]]$fp,
      hivdemo_proj = hivdemo_proj_list[[cnt]],
      pmtct = pmtct_1,
      year = c(2015:2023),
      age = c("15-24", "25-34", "35-49", "50-99"),
      sex = c("female")
    )
  print(11)
  simul_b_counter <-
    simul_aware_agg(
      samp = samp_1,
      mod = make_country[[cnt]]$mod,
      fp = make_country[[cnt]]$fp,
      hivdemo_proj = hivdemo_proj_list[[cnt]],
      pmtct = pmtct_1,
      year = c(2015:2023),
      age = c("15-24", "25-34", "35-49", "50-99"),
      sex = c("male", "female")
    )
  print(12)
  
  aware_agg_simul_male_counter[[cnt]]$out_simul_aware_all = simul_m_counter
  aware_agg_simul_female_counter[[cnt]]$out_simul_aware_all = simul_f_counter
  aware_agg_simul_both_counter[[cnt]]$out_simul_aware_all = simul_b_counter
  
  make_country[[cnt]]$aware_male_counter$out_simul_aware_all = simul_m_counter
  make_country[[cnt]]$aware_female_counter$out_simul_aware_all = simul_f_counter
  make_country[[cnt]]$aware_both_counter$out_simul_aware_all = simul_b_counter
  
  gc()
}

saveRDS(
  object = make_country,
  file = here::here('data/make_country_simu_final_readme.rds')
)


```
----
goal: visualizes time to diagnoses, awarness, and proportion unaware
estimate: ~ 5 seconds 
comments: all other graphs are aggregates (pooled or geospacial) or derivatives (ttd difference) of the following 3 graphs
comments2: if you would like all the graphs in the paper 3.0-3.6 provides all manuscirpt and supplemental 1 graphs, 4.0 provides supplemental 2 (alongside 4.1, svg vs word) but these require original sets of PJNZ files
outputs: time to diagnoses, number unaware, and proportion status awareness, compare to data_visualization files
----
```{r graphing}

cnt = "Synthetic"
# graph the total tests from 2015 to 2023
# plots time to diagnoses for Malawi for both counterfactual and observed 
counterfactual_ttd(make_country, cnt)

# plots awareness
counter_awareness(make_country, cnt)

# plot number unaware
counter_unaware(make_country,cnt)

```