---
  output: github_document
---
  
  
----
goal: download and install required packages, load source files
estimate: 
```{r setup, include = FALSE}
packages <- c(
  "scales", "tidyverse", "rnaturalearth", "rnaturalearthdata",
  "sf", "ggnewscale", "devtools", "data.table", "Matrix", "Rcpp",
  "stringi", "ggh4x", "forcats", "ggtext", "terra", "gridExtra"
)
to_install <- packages[!packages %in% installed.packages()[, "Package"]]

if (length(to_install) > 0) {
  install.packages(to_install)
}
# load all packages
invisible(lapply(packages, library, character.only = TRUE))

# download and set up first 90 package
# first90
if(!"first90" %in% installed.packages()[, "Package"]){
 devtools::install_github("mrc-ide/first90release")
}
library(first90)

# source functions
source(here::here("anc testing/0.1 extracting pjnz functions.R"))
source(here::here("anc testing/0.4 functions.R"))
source(here::here("anc testing/0.5 simul-aware-functions.R"))
source(here::here("anc testing/0.6 time dx functions.R"))

source(here::here("anc testing/1.0 simmod.R"))
source(here::here("anc testing/1.1 tot test out.R"))


```


UNAIDS put forward the ambitious 90-90-90 target to end the AIDS epidemic by 2030. This target aims for 90% of people living with HIV (PLHIV) to be aware of their HIV-positive status, 90% of those diagnosed to receive antiretroviral therapy, and 90% of those on treatment to have a suppressed viral load by 2020 (each reaching 95% by 2030).
HIV testing remains an important bottleneck in this cascade, however, and obtaining reliable epidemiological data on the proportion of PLHIV aware of their status is difficult.
Such information is nevertheless crucial to effectively monitor HIV prevention efforts. Tracking progress towards achievement of this “first 90” target could be improved by combining population-based surveys and programmatic data on the number of HIV tests performed (and yield) in a coherent deterministic/statistical model. 
This type of integrative systems modelling is especially useful to fully consider HIV incidence, mortality, testing behaviours, as well as to coherently combine different sources of data. 

The goal of shiny90 is to provide annual estimates of the proportion of PLHIV that are aware of their status, by combining estimates of PLHIV from EPP/Spectrum, annual programmatic data on the number of HIV tests performed (and yield), and nationally-representative survey of HIV testing behaviors. 

This is an update to Shiny90 to include ANC estimates for the publication " The Impact of Declining HIV Testing in Africa on Time to HIV Diagnosis and Awareness of HIV Status: A Modeling Study of Population-Based Surveys and HIV Testing Program Data (2015-2023) "

## Installation Example: Synthetic (based on Malawi)
runtime : variable - depends on installation status

comment: for using non synthetic files use "ReadMe - real PJNZ
```{r inital loading, fig.height = 8, fig.width = 8, warning = FALSE}

# load pre cleaned synthethic file
Synthetic <- readRDS(here::here("anc testing/example files.rds"))

# align naming scheme with files
make_country <- list()
make_country$Synthetic <- Synthetic$make_country

pmtct_list <- list()
pmtct_list$Synthetic <- Synthetic$pmtct

hivdemo_proj_list <- list()
hivdemo_proj_list$Synthetic <- Synthetic$demo_proj 

# extract fp 
fp <- make_country$Synthetic$fp

# We visualize the PJNZ data
first90::plot_pjnz(fp)

#define input data
age_group <- c('15-24','25-34','35-49')
cnt = make_country$Synthetic$cnt

# define clean suvery and program Synthetic
dat <- first90::select_hts(make_country$Malawi$survey_hts, cnt, age_group)

prg_dat <- first90::select_prgmdata(make_country$Synthetic$prgm_dat, cnt, age_group)

# We visualize the program data
first90::plot_inputdata(prg_dat, fp)

```

estimate: 797 seconds

```{r, fig.height = 10, fig.width = 8.5, warning = FALSE}
tic()

# here the running of the simulation commences (examine 2.0 simulating Shiny90.R)

# define path
path_anc <- here::here("anc testing")

# select which country you want to run - in this case Malawi
country = make_country$Synthetic

# confirm
cnt = country$cnt
print(cnt)
age_group <- c('15-24','25-34','35-49')

# extract fp and data
fp <- make_country[[cnt]]$fp
pgrm_dat <- first90::select_prgmdata(make_country[[cnt]]$prgm_dat, cnt = cnt)
survey_hts <- first90::select_hts(make_country[[cnt]]$survey_hts,
                                  cnt = cnt,
                                  age_group = age_group)

# from 0.2 create PMTCT and HIV demoproj, Preventing monther to child and demographic projection information
# select country specific pmtct
pmtct <- pmtct_list[[cnt]]


# select country specific demo proj
hivdemo_proj <- hivdemo_proj_list[[cnt]]


# the shiny90-ANC used 3 more parameters than Shiny90 add them manually( for now)
theta1

# create an initial projection
fp <- create_anc_param(
  theta = theta1,
  fp = fp,
  pmtct = pmtct,
  hivdemo_proj = hivdemo_proj,
  verbose = T
)

# curate data for likelihood from the inital projection, Avoids double counting
likdat <- prepare_anc_likdat(dat_evertest = survey_hts,
                             dat_prg = pgrm_dat,
                             fp = fp)

# estimate initial liklihood 
ll_hts_anc(
  theta = theta1,
  fp = fp,
  likdat = likdat,
  pmtct = pmtct,
  hivdemo_proj = hivdemo_proj,
  verboise = T
)

# preoptimization with Nelder-Mead to find BFGS start point (adjust based on country)
# required as BFGS can at times get lost in decision space
opt <- optim(
  theta1,
  ll_hts_anc,
  fp = fp,
  likdat = likdat,
  pmtct = pmtct,
  hivdemo_proj = hivdemo_proj,
  method = "Nelder-Mead",
  control = list(
    fnscale = -1,
    trace = 4,
    REPORT = 1,
    maxit = 1000
  )
)

# isolate optmized parameters
theta1 = opt$par

# recreate inital param from post nelder-mead
fp <- create_anc_param(
  theta = theta1,
  fp = fp,
  pmtct = pmtct,
  hivdemo_proj = hivdemo_proj,
  verbose = T
)
# recreate likdat
likdat <- prepare_anc_likdat(dat_evertest = survey_hts,
                             dat_prg = pgrm_dat,
                             fp = fp)

#use independent opt1 vs opt again here to prevent some bugs
# BFGS much better at finalizing the optimization
opt1 <- optim(
  theta1,
  ll_hts_anc,
  fp = fp,
  likdat = likdat,
  pmtct = pmtct,
  hivdemo_proj = hivdemo_proj,
  method = "BFGS",
  control = list(
    fnscale = -1,
    trace = 4,
    REPORT = 1,
    maxit = 550
  ),
  hessian = T
)

# reset the opt1 to opt for future steps
opt = opt1

# confirm reasonable values for opt
optimized_par_anc(opt)

# confirm liklihood matches with optim run ( an is reasonable)
ll_hts_anc(
  theta = opt$par,
  fp = fp,
  likdat = likdat,
  pmtct = pmtct,
  hivdemo_proj = hivdemo_proj,
  verboise = T
)

# fp and mod from optimized parameters
fp <- create_anc_param(
  theta = opt$par,
  fp = fp,
  pmtct = pmtct,
  hivdemo_proj = hivdemo_proj
)
mod <- simmod_anc_t(fp)
toc()
```


estimate 224 seconds
```{r credible intervals}
tic()
# identify credible intervals
simul <- simul.test.anc(
  opt = opt,
  fp = fp,
  likdat = likdat,
  pmtct = pmtct,
  hivdemo_proj = hivdemo_proj,
  sim = 3000
)

# save both the simul and the sample( useful for counterfactual analysis)
samp = simul$samp
simul = simul$simul

# obtaining outputs and plotting them
make_country[[cnt]]$mod <- mod
make_country[[cnt]]$fp <- fp
make_country[[cnt]]$simul <- simul
make_country[[cnt]]$out_evertest <- get_out_evertest(mod, fp)
make_country[[cnt]]$opt <- opt
make_country[[cnt]]$samp <- samp

# save the file
saveRDS(object = make_country, file = here::here('anc testing/data/make_country_simul_readme.rds'))
toc()
```

The model fits by age and sex.
a more dealited example is provided in appendix-paper-creation which will provide model fits to age,sex and HIV status ( and to program data by ANC and non-ANC)
```{r, fig.height = 5, fig.width = 8.5, warning=FALSE}

# create a survey plot of all 6 age and sex groups

source("0.7 graphing functions.R")

# this should have the full malawi simulation file from the prior steps
survey_fit_all(make_country,cnt = "Synthetic")

survey_fit_postive(make_country,cnt = "Synthetic")


```

# create counterfactual
estimate 236 seconds
```{r, fig.height = 5, fig.width = 5, warning = FALSE}
tic()
# create a counterfactual
source("2.1 counterfactual creation.R")
# this fucntion resets cnt need to readd malawi
cnt = "Synthetic"

#load the files
counter_years <- readRDS("data/counter_years.rds")
counter_anc_years <- readRDS("data/counter_years.rds")


# repeat many of the inital steps, which are now saved in make country
fp <- make_country[[cnt]]$fp
pgrm_dat <- first90::select_prgmdata(make_country[[cnt]]$prgm_dat, cnt = cnt)
survey_hts <- first90::select_hts(make_country[[cnt]]$survey_hts,
                                  cnt = cnt,
                                  age_group <- c('15-24', '25-34', '35-49'))
mod = make_country[[cnt]]$mod
opt = make_country[[cnt]]$opt

# select country specific pmtct
pmtct <- pmtct_list[[cnt]]

# select country specific demo proj
hivdemo_proj <- hivdemo_proj_list[[cnt]]


# we saved the sample in the full run now we use it again( for creation of a counterfactual simulation)
samp = make_country[[cnt]]$samp

# specifies that we only care about Malawi
counter_years_loop = counter_years[counter_years$country == cnt, ]
counter_years_loop <- counter_years_loop[!is.na(counter_years_loop$country),]

#clear all counter factual sample and pmtct
samp_1 = NULL
pmtct_1 = NULL

if (!is.na(counter_years_loop$start)) {
  
  # Apply counterfactual opperation to every row of samp
  samp_new <- function(samp, counter_years_loop) {
    stopifnot(is.matrix(samp) || is.data.frame(samp))
    
    samp <- as.matrix(samp)
    
    convert <- (ncol(samp) - 4) / 2
    
    start <- as.numeric(counter_years_loop[2])
    
    # if NA, end becomes 30(ie no recovery)
    end <- as.numeric(ifelse(!is.na(counter_years_loop[3]), (
      as.numeric(counter_years_loop[3]) - 30 - 1
    ), 30))
    
    start_female <- start - 30
    start_dx     <- convert + (start - 40)
    end_dx       <- start_dx + (end - start_female)
    
    clamp <-
      function(i)
        max(1, min(ncol(samp), as.integer(i)))
    
    sf <- clamp(start_female)
    e1 <- clamp(min(end, convert))
    
    sd <- clamp(start_dx)
    e2 <- clamp(min(end_dx, convert + convert - 10))
    
    # apply to all rows
    if (sf <= e1)
      samp[, sf:e1] <- samp[, sf]
    if (sd <= e2)
      samp[, sd:e2] <- samp[, sd]
    
    samp
  }
  if (!is.na(counter_years_loop$start)) {
    samp_1 = samp_new(samp, counter_years_loop)
  } else{
    print("non-counter samp")
    samp_1 = samp
  }
  if (is.na(counter_years_loop$start) &
      is.na(counter_years_loop[1:3]$start)) {
    print("skipping")
    next
  }
  
  #counterfactual ANC
  
  start_anc = counter_years_loop$start
  
  names(pmtct$anc_test) = as.character(2000:2030)
  names(pmtct$needpmtct) = as.character(1970:2030)
  names(pmtct$receivepmtct) = as.character(1970:2030)
  
  pmtct_1 = pmtct
  
  # find the number of years which have data, using testing data
  anc_indx_years <-
    pmtct$anc_test[!is.na(pmtct$anc_test[2, ])]
  anc_data_years <-
    as.integer(names(pmtct$anc_test)[!(is.na(pmtct$anc_test[2, ]) |
                                         pmtct$anc_test[2, ] == 0)])
  anc_data_idx <-
    fp$ss$PROJ_YEARS - ((fp$ss$PROJ_YEARS + 1970 - 1) - anc_data_years)
  
  # Find valid columns where row 2 is not NA
  valid_cols <-
    which(!(is.na(pmtct$anc_test[2, ]) |
              pmtct$anc_test[2, ] == 0))  # Faster than repeated indexing
  
  # anc tested and tested anc pos
  anc_tested <-
    as.integer(colSums(pmtct$anc_test[c(2, 5), valid_cols], na.rm = T))
  anc_pos <- as.integer(pmtct$anc_test[3, valid_cols])
  
  # Extract birth indices
  births_idx <- colnames(pmtct$anc_test)[valid_cols]
  
  # Compute ANC coverage,  nb women tested at anc1 / births
  anc_cov <- anc_tested / pmtct$births[births_idx]
  
  # Compute ANC positive proportion
  anc_pos_prop <- anc_pos / anc_tested
  
  anc_tests_prob = as.numeric(pmtct$receivepmtct) / as.numeric(pmtct$needpmtct)
  anc_tests_prob[is.na(anc_tests_prob)] <- 0
  names(anc_tests_prob) <-
    fp$ss$proj_start:(fp$ss$proj_start + fp$ss$PROJ_YEARS - 1)
  
  #if (any(anc_tests_prob > 1)) { print("check spectrum's pmtct inputs, prob of being tested at anc >100%") }
  anc_tests_prob[anc_tests_prob > 1] <-
    0.999 # or we could put a default of 95% (to discuss)
  
  # linear interpolation to remove any missing data
  if (length(anc_cov) != 0) {
    # apply known data
    anc_tests_prob[anc_data_idx] <- anc_cov
    
    # predict using artcov method past the date (for projection)
    anc_tests_prob[max(anc_data_idx):fp$ss$PROJ_YEARS] <-
      anc_tests_prob[max(anc_data_idx):fp$ss$PROJ_YEARS]
    
    
  }
  # identify years when ANC should be applied
  Years_anc = names(which(anc_tests_prob[start_anc] > anc_tests_prob[start_anc:61]))
  year_start = names(anc_tests_prob[start_anc])
  #fixes some issues with country files
  
  
  if (length(Years_anc) > 0) {
    # adjust anctest
    pmtct_1$anc_test[, Years_anc] = pmtct$anc_test[, year_start]
    # if needed adjust recive/need pmtct, all countries should have anctest but just incase one year is missing.
    pmtct_1$receivepmtct[Years_anc] = pmtct$receivepmtct[year_start]
    pmtct_1$needpmtct[Years_anc] = pmtct$needpmtct[year_start]
  }
}

# run to create the counterfactual fp
fp = create_anc_param(opt$par, fp, pmtct, hivdemo_proj)


# identify credible intervals of counterfactual (need fp)
counter_simul <- simul.run.anc(samp_1, fp, pmtct = pmtct_1, hivdemo_proj = hivdemo_proj)

#save counterfactual
make_country[[cnt]]$counter_simul = counter_simul
make_country[[cnt]]$counter_samp = samp_1

# save again 
saveRDS(
  object = make_country,
  file = here::here('anc testing/data/make_country_simu_final_readme.rds')
)
toc()
```
esimate: 1191
```{r time to diagnoses}
tic()
cnt = "Synthetic"

# this functions by creating a counterfactual sample then runnign all time to diangoses on that sample and 

#define time to diagnoses lists
tdx_agg_simul_male = list()
tdx_agg_simul_female = list()
tdx_agg_simul_both = list()

tdx_agg_simul_male_counter = list()
tdx_agg_simul_female_counter = list()
tdx_agg_simul_both_counter = list()

aware_agg_simul_male = list()
aware_agg_simul_female = list()
aware_agg_simul_both = list()

aware_agg_simul_male_counter = list()
aware_agg_simul_female_counter = list()
aware_agg_simul_both_counter = list()

# cannot run chad without changing see 2.3 time to diangoses
# ensure it is still malawi
print(cnt)

#ensure all data frames are clean
simul_b_counter = NULL
simul_b_counter = NULL
simul_b_counter = NULL

simul_f = NULL
simul_m = NULL
simul_b = NULL

simul_tdxM_counter = NULL
simul_tdxF_counter = NULL
simul_tdxB_counter = NULL

simul_tdxM = NULL
simul_tdxF = NULL
simul_tdxB = NULL


# define variable again
fp <- make_country[[cnt]]$fp

pgrm_dat <-
  first90::select_prgmdata(make_country[[cnt]]$prgm_dat, cnt = cnt)

survey_hts <-
  first90::select_hts(
    make_country[[cnt]]$survey_hts,
    cnt = cnt,
    age_group = c('15-24', '25-34', '35-49')
  )

# define parameters by country
samp = make_country[[cnt]]$samp
opt = make_country[[cnt]]$opt
mod = make_country[[cnt]]$mod

# we select pmtct data
pmtct <- pmtct_list[[cnt]]

names(pmtct$receivepmtct) = as.character(1970:2030)
names(pmtct$needpmtct) = as.character(1970:2030)

# we select HIV demo proj
hivdemo_proj <- hivdemo_proj_list[[cnt]]

# repeat again to create a new counterfatual sample
#clear all counter factual sample and pmtct
samp_1 = NULL
pmtct_1 = NULL

if (!is.na(counter_years_loop$start)) {
  
  samp_1 <- make_country[[cnt]]$counter_samp
  
  #counterfactual ANC
  start_anc = counter_years_loop$start
  
  names(pmtct$anc_test) = as.character(2000:2030)
  names(pmtct$needpmtct) = as.character(1970:2030)
  names(pmtct$receivepmtct) = as.character(1970:2030)
  
  pmtct_1 = pmtct
  
  # find the number of years which have data, using testing data
  anc_indx_years <-
    pmtct$anc_test[!is.na(pmtct$anc_test[2, ])]
  anc_data_years <-
    as.integer(names(pmtct$anc_test)[!(is.na(pmtct$anc_test[2, ]) |
                                         pmtct$anc_test[2, ] == 0)])
  anc_data_idx <-
    fp$ss$PROJ_YEARS - ((fp$ss$PROJ_YEARS + 1970 - 1) - anc_data_years)
  
  # Find valid columns where row 2 is not NA
  valid_cols <-
    which(!(is.na(pmtct$anc_test[2, ]) |
              pmtct$anc_test[2, ] == 0))  # Faster than repeated indexing
  
  # anc tested and tested anc pos
  anc_tested <-
    as.integer(colSums(pmtct$anc_test[c(2, 5), valid_cols], na.rm = T))
  anc_pos <- as.integer(pmtct$anc_test[3, valid_cols])
  
  # Extract birth indices
  births_idx <- colnames(pmtct$anc_test)[valid_cols]
  
  # Compute ANC coverage,  nb women tested at anc1 / births
  anc_cov <- anc_tested / pmtct$births[births_idx]
  
  # Compute ANC positive proportion
  anc_pos_prop <- anc_pos / anc_tested
  
  anc_tests_prob = as.numeric(pmtct$receivepmtct) / as.numeric(pmtct$needpmtct)
  anc_tests_prob[is.na(anc_tests_prob)] <- 0
  names(anc_tests_prob) <-
    fp$ss$proj_start:(fp$ss$proj_start + fp$ss$PROJ_YEARS - 1)
  
  #if (any(anc_tests_prob > 1)) { print("check spectrum's pmtct inputs, prob of being tested at anc >100%") }
  anc_tests_prob[anc_tests_prob > 1] <-
    0.999 # or we could put a default of 95% (to discuss)
  
  # linear interpolation to remove any missing data
  if (length(anc_cov) != 0) {
    # apply known data
    anc_tests_prob[anc_data_idx] <- anc_cov
    
    # predict using artcov method past the date (for projection)
    anc_tests_prob[max(anc_data_idx):fp$ss$PROJ_YEARS] <-
      anc_tests_prob[max(anc_data_idx):fp$ss$PROJ_YEARS]
    
    
  }
  # identify years when ANC should be applied
  Years_anc = names(which(anc_tests_prob[start_anc] > anc_tests_prob[start_anc:61]))
  year_start = names(anc_tests_prob[start_anc])
  #fixes some issues with country files
  
  
  if (length(Years_anc) > 0) {
    # adjust anctest
    pmtct_1$anc_test[, Years_anc] = pmtct$anc_test[, which(names(pmtct$anc_test) %in% year_start)]
    # if needed adjust recive/need pmtct, all countries should have anctest but just incase one year is missing.
    pmtct_1$receivepmtct[which(names(pmtct$anc_test) %in% Years_anc)] = pmtct$receivepmtct[which(names(pmtct$anc_test) %in% year_start)]
    pmtct_1$needpmtct[which(names(pmtct$anc_test) %in% Years_anc)] = pmtct$needpmtct[which(names(pmtct$anc_test) %in% year_start)]
  }
}


# time to diagnosis
simul_tdxF = simul_pool_time_dx_agg_prev(
  samp = samp,
  mod = make_country[[cnt]]$mod,
  fp = make_country[[cnt]]$fp,
  hivdemo_proj = hivdemo_proj_list[[cnt]],
  pmtct = pmtct_list[[cnt]],
  year = 2015:2023,
  std = F,
  age = c("15-24", "25-34", "35-49", "50-99"),
  sex = "female",
  parallel = T
)
print(1)
simul_tdxM = simul_pool_time_dx_agg_prev(
  samp = samp,
  mod = make_country[[cnt]]$mod,
  fp = make_country[[cnt]]$fp,
  hivdemo_proj = hivdemo_proj_list[[cnt]],
  pmtct = pmtct_list[[cnt]],
  year = 2015:2023,
  std = F,
  age = c("15-24", "25-34", "35-49", "50-99"),
  sex = "male",
  parallel = T
)

print(2)

simul_tdxB = simul_pool_time_dx_agg_prev(
  samp = samp,
  mod = make_country[[cnt]]$mod,
  fp = make_country[[cnt]]$fp,
  hivdemo_proj = hivdemo_proj_list[[cnt]],
  pmtct = pmtct_list[[cnt]],
  year = 2015:2023,
  std = F,
  age = c("15-24", "25-34", "35-49", "50-99"),
  sex = c("male", "female"),
  parallel = T
)
print(3)

tdx_agg_simul_male[[cnt]]$out_simul_tdx_all = simul_tdxM
tdx_agg_simul_female[[cnt]]$out_simul_tdx_all = simul_tdxF
tdx_agg_simul_both[[cnt]]$out_simul_tdx_all = simul_tdxB

make_country[[cnt]]$tdx_male$out_simul_tdx_all = simul_tdxM
make_country[[cnt]]$tdx_female$out_simul_tdx_all = simul_tdxF
make_country[[cnt]]$tdx_both$out_simul_tdx_all = simul_tdxB

# saveRDS(tdx_agg_simul_male,
#         paste0(here::here("outputs"),
#                "/male time to dx.rda"))
# saveRDS(tdx_agg_simul_female,
#         paste0(here::here("outputs"),
#                "/female time to dx.rda"))
# saveRDS(tdx_agg_simul_both,
#         paste0(here::here("outputs"),
#                "/both time to dx.rda"))
gc()


# counterfactual time to diagnosis
if (!(is.null(samp_1))) {
  simul_tdxF_counter = simul_pool_time_dx_agg_prev(
    samp = samp_1,
    mod = make_country[[cnt]]$mod,
    fp = make_country[[cnt]]$fp,
    hivdemo_proj = hivdemo_proj_list[[cnt]],
    pmtct = pmtct_1,
    year = 2015:2023,
    std = F,
    age = c("15-24", "25-34", "35-49", "50-99"),
    sex = "female",
    parallel = T
  )
  
  print(4)
  
  simul_tdxM_counter = simul_pool_time_dx_agg_prev(
    samp = samp_1,
    mod = make_country[[cnt]]$mod,
    fp = make_country[[cnt]]$fp,
    hivdemo_proj = hivdemo_proj_list[[cnt]],
    pmtct = pmtct_1,
    year = 2015:2023,
    std = F,
    age = c("15-24", "25-34", "35-49", "50-99"),
    sex = "male",
    parallel = T
  )
  
  print(5)
  
  simul_tdxB_counter = simul_pool_time_dx_agg_prev(
    samp = samp_1,
    mod = make_country[[cnt]]$mod,
    fp = make_country[[cnt]]$fp,
    hivdemo_proj = hivdemo_proj_list[[cnt]],
    pmtct = pmtct_1,
    year = 2015:2023,
    std = F,
    age = c("15-24", "25-34", "35-49", "50-99"),
    sex = c("male", "female"),
    parallel = T
  )
  
  print(6)
  
  tdx_agg_simul_male_counter[[cnt]]$out_simul_tdx_all = simul_tdxM_counter
  tdx_agg_simul_female_counter[[cnt]]$out_simul_tdx_all = simul_tdxF_counter
  tdx_agg_simul_both_counter[[cnt]]$out_simul_tdx_all = simul_tdxB_counter
  
  make_country[[cnt]]$tdx_male_counter$out_simul_tdx_all = simul_tdxM_counter
  make_country[[cnt]]$tdx_female_counter$out_simul_tdx_all = simul_tdxF_counter
  make_country[[cnt]]$tdx_both_counter$out_simul_tdx_all = simul_tdxB_counter
  
  # saveRDS(tdx_agg_simul_male_counter,
  #         paste0(here::here("outputs"), "/male time to dx counter.rda"))
  # saveRDS(
  #   tdx_agg_simul_female_counter,
  #   paste0(here::here("outputs"), "/female time to dx counter.rda")
  # )
  # saveRDS(tdx_agg_simul_both_counter,
  #         paste0(here::here("outputs"), "/both time to dx counter.rda"))
  gc()
}

simul_m <-
  simul_aware_agg(
    samp = samp,
    mod = make_country[[cnt]]$mod,
    fp = make_country[[cnt]]$fp,
    hivdemo_proj = hivdemo_proj_list[[cnt]],
    pmtct = pmtct_list[[cnt]],
    year = c(2015:2023),
    age = c("15-24", "25-34", "35-49", "50-99"),
    sex = c("male")
  )
print(7)
simul_f <-
  simul_aware_agg(
    samp = samp,
    mod = make_country[[cnt]]$mod,
    fp = make_country[[cnt]]$fp,
    hivdemo_proj = hivdemo_proj_list[[cnt]],
    pmtct = pmtct_list[[cnt]],
    year = c(2015:2023),
    age = c("15-24", "25-34", "35-49", "50-99"),
    sex = c("female")
  )
print(8)
simul_b <-
  simul_aware_agg(
    samp = samp,
    mod = make_country[[cnt]]$mod,
    fp = make_country[[cnt]]$fp,
    hivdemo_proj = hivdemo_proj_list[[cnt]],
    pmtct = pmtct_list[[cnt]],
    year = c(2015:2023),
    age = c("15-24", "25-34", "35-49", "50-99"),
    sex = c("male", "female")
  )
print(9)

aware_agg_simul_male[[cnt]]$out_simul_aware_all = simul_m
aware_agg_simul_female[[cnt]]$out_simul_aware_all = simul_f
aware_agg_simul_both[[cnt]]$out_simul_aware_all = simul_b

make_country[[cnt]]$aware_male$out_simul_aware_all = simul_m
make_country[[cnt]]$aware_female$out_simul_aware_all = simul_f
make_country[[cnt]]$aware_both$out_simul_aware_all = simul_b

# saveRDS(aware_agg_simul_male, paste0(here::here("outputs"), "/male aware.rda"))
# saveRDS(aware_agg_simul_female,
#         paste0(here::here("outputs"), "/female aware.rda"))
# saveRDS(aware_agg_simul_both, paste0(here::here("outputs"), "/both aware.rda"))
gc()

# counterfactual simul
if (!(is.null(samp_1))) {
  simul_m_counter <-
    simul_aware_agg(
      samp = samp_1,
      mod = make_country[[cnt]]$mod,
      fp = make_country[[cnt]]$fp,
      hivdemo_proj = hivdemo_proj_list[[cnt]],
      pmtct = pmtct_1,
      year = c(2015:2023),
      age = c("15-24", "25-34", "35-49", "50-99"),
      sex = c("male")
    )
  
  print(10)
  
  simul_f_counter <-
    simul_aware_agg(
      samp = samp_1,
      mod = make_country[[cnt]]$mod,
      fp = make_country[[cnt]]$fp,
      hivdemo_proj = hivdemo_proj_list[[cnt]],
      pmtct = pmtct_1,
      year = c(2015:2023),
      age = c("15-24", "25-34", "35-49", "50-99"),
      sex = c("female")
    )
  print(11)
  simul_b_counter <-
    simul_aware_agg(
      samp = samp_1,
      mod = make_country[[cnt]]$mod,
      fp = make_country[[cnt]]$fp,
      hivdemo_proj = hivdemo_proj_list[[cnt]],
      pmtct = pmtct_1,
      year = c(2015:2023),
      age = c("15-24", "25-34", "35-49", "50-99"),
      sex = c("male", "female")
    )
  print(12)
  
  aware_agg_simul_male_counter[[cnt]]$out_simul_aware_all = simul_m_counter
  aware_agg_simul_female_counter[[cnt]]$out_simul_aware_all = simul_f_counter
  aware_agg_simul_both_counter[[cnt]]$out_simul_aware_all = simul_b_counter
  
  make_country[[cnt]]$aware_male_counter$out_simul_aware_all = simul_m_counter
  make_country[[cnt]]$aware_female_counter$out_simul_aware_all = simul_f_counter
  make_country[[cnt]]$aware_both_counter$out_simul_aware_all = simul_b_counter
  
  # saveRDS(aware_agg_simul_male_counter,
  #         paste0(here::here("outputs"), "/male aware counter.rda"))
  # saveRDS(aware_agg_simul_female_counter,
  #         paste0(here::here("outputs"), "/female aware counter.rda"))
  # saveRDS(aware_agg_simul_both_counter,
  #         paste0(here::here("outputs"), "/both aware counter.rda"))
  gc()
}

saveRDS(
  object = make_country,
  file = here::here('anc testing/data/make_country_simu_final_readme.rds')
)

toc()
```

#you now have all the data needed for graphing, below is a graph of total testing and then by time to diangoses and awareness

# if you would like all the graphs in the paper the 3.0-3.6 provides all manuscirpt and supplemental 1 graphs, 4.0 provides supplemental 2 (alongside 4.1, svg vs word)

```{r graphing}

cnt = "Synthetic"
source(paste0(path_anc, "/1.1 tot test out.R"))

# graph the total tests from 2015 to 2023

# total vct tests
graph_tot_tests(
  make_country[[cnt]],
  cnt = cnt,
  sex = "both",
  hivstatus = "all",
  test_type = "vcttests",
  year_start = 2000,
  year_end = 2023
)
# total VCT positives
graph_tot_tests(
  make_country[[cnt]],
  cnt = cnt,
  sex = "both",
  hivstatus = "positive",
  test_type = "vcttests",
  year_start = 2000,
  year_end = 2023
)



# total ANC
graph_tot_tests(
  make_country[[cnt]],
  cnt = cnt,
  sex = "both",
  hivstatus = "all",
  test_type = "anctests",
  year_start = 2000,
  year_end = 2023
)

# total ANC positives
graph_tot_tests(
  make_country[[cnt]],
  cnt = cnt,
  sex = "both",
  hivstatus = "positive",
  test_type = "anctests",
  year_start = 2000,
  year_end = 2023
)

source("0.7 graphing functions.R")
source("0.6 time dx functions.R")
# plots time to diagnoses for Malawi for both counterfactual and observed 
counterfactual_ttd(make_country, cnt)

# plots awareness
counter_awareness(make_country, cnt)

# plot number unaware
counter_unaware(make_country,cnt)

```